% paras.tex - examples of paragraph formatting and special paragraph
%             environments

% Andrew Roberts - September 2003

\documentclass[english]{article}

\usepackage{babel}
\usepackage{times}
\usepackage{alltt}
\usepackage{moreverb}

\begin{document}

\title{Latex Tutorial 7 (Formatting) Examples}
\author{Andrew Roberts}
\maketitle

\section{Paragraph Formatting}

\begin{flushleft}
\texttt{Flushleft} is the default justification for a typical word
processor.  It looks considerably less tidy than Latex's default full
justified paragraphs
\end{flushleft}

\begin{flushright}
\texttt{Flushright} does not the most useful alignment for basic
paragraphs.  Has more use wi \end{flushright}

\begin{center}
The \texttt{center} has been seen many times in various examples from
previous examples, although usually to align tables and figures, rather
than text --- it works for all though!
\end{center}

\section{Special Paragraph Environments}
\subsection{Verbatim}

\begin{verbatim}
The verbatim environment
  simply reproduces every
 character you input,
including all  s p a c e s!
\end{verbatim}

\subsection{alltt}
\begin{alltt}
Verbatim extended with the ability
to use normal commands.  Therefore, it
is possible to \emph{emphasize} words in
this environment, for example.
\end{alltt}

\subsection{Listing}

\begin{listing}[2]{2}
The first line,
the second line,
the third line,
the forth line,
and so on...
\end{listing}

\subsection{Quote and Quotation}

Lots of text. Lots of text. Lots of text. Lots of text. Lots of text.
Lots of text. Lots of text. Lots of text. Lots of text. Lots of text.

\begin{quote}
I can resist everything except temptation. \emph{(Oscar Wilde)}
\end{quote}

Lots of text. Lots of text. Lots of text. Lots of text. Lots of text.
Lots of text. Lots of text. Lots of text. Lots of text. Lots of text.
\begin{quotation} Roast beef and Yorkshire,
or roast pork and apple sauce, followed up by suet pudding and driven
home, as it were, by a cup of mahogany-brown tea, have put you in just
the right mood\ldots In these blissful circumstances, what is it that
you want to read about?

Naturally, about a murder.
\end{quotation}


\subsection{Verse}

Lyrics of 'I Am The Walrus' by \emph{The Beatles}.

\begin{verse}
I am he as you are he as you are me and we are all together \\
See how they run like pigs from a gun see how they fly \\
I'm crying \\
Sitting on a cornflake \\
Waiting for the van to come \\
Corporation T-shirt, stupid bloody Tuesday \\
Man you've been a naughty boy you let your face grow long

I am the eggman \\
They are the eggmen \\
I am the walrus \\
Goo goo g' joob

\ldots
\end{verse}

\end{document}
